Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-18 WSSSPE3/report/wg_main_publishing_SW.tex
small edits

\textbf{Reproducibility}: Part of the purpose of these executable paper venues
is to (at least partially) address the reproducibility issue by making a paper
itself recompute its own results.

@@

The plan is to create a web page describing executable papers, their values, and
a list of what publishers support them. \katznote{when?}

>>>>

\textbf{Reproducibility}: Part of the purpose of these executable paper venues
is to (at least partially) address the reproducibility issue by making paper
recompute their own results.

@@

The plan is to create a web page describing executable papers, their value, and
a list of what publishers support them. \katznote{when?}
